Preparing for Potential Closure of European Airspaces due to Re-entering Space Objects

### 2025-06-07 paper.qmd
address observation from Reviewer 5 about missing keywords

@@

format:
  ieee-pdf:
    keep-tex: true
    colorlinks: false
    # fig-pos: 'H'
    journaltype: conference
    papersize: a4
    include-in-header:
      - file: media/preamble.tex
    include-before-body:
      - text: |
          \let\qty\SI
          % NOTE: make siunitx's \qty work without clashing with the one in physics
  ieee-html: 
    html-math-method: mathjax
    include-in-header:
      file: media/siunitx.html
author:
  - id: es
    name: Enrico Spinielli
    affiliations:
      - ref: aiu
    orcid: 0000-0001-8584-9131
    email: enrico.spinielli@eurocontrol.int
    attributes:
      corresponding: true
    role: 
      - conceptualization
      - software
  - name: Rainer Koelle
    affiliations:
      - ref: aiu
    orcid: 0000-0003-2810-1404
    email: rainer.koelle@eurocontrol.int
    role: 
      - editing
  - name: Quinten Goens
    affiliations:
      - ref: aiu
    orcid: 0000-0003-2187-1924
    email: quinten.goens@eurocontrol.int
    role: 
      - editing
affiliations:
  - id: aiu
    name: EUROCONTROL
    department: Aviation Intelligence Unit
    city: Brussels
    country: Belgium
  - id: fake
    name: ACME
    department: Best Tricks
    city: Los Angeles
    country: USA
bibliography: media/references.bib
acronyms:
  insert_loa: false
  fromfile:
    - ./media/acronyms.yml
editor: 
  markdown: 
    wrap: 72
---
```{r}
```

>>>>

keywords: 
  - space debris
  - airspace closure
  - aviation safety

@@

format:
  ieee-pdf:
    keep-tex: true
    colorlinks: false
    # fig-pos: 'H'
    journaltype: conference
    papersize: a4
    include-in-header:
      - file: media/preamble.tex
    include-before-body:
      - text: |
          \let\qty\SI
          % NOTE: make siunitx's \qty work without clashing with 
          %      the one in physics
  ieee-html: 
    html-math-method: mathjax
    include-in-header:
      file: media/siunitx.html
author:
  - id: es
    name: Enrico Spinielli
    affiliations:
      - ref: aiu
    orcid: 0000-0001-8584-9131
    email: enrico.spinielli@eurocontrol.int
    attributes:
      corresponding: true
    role: 
      - conceptualization
      - writing
      - software
  - name: Rainer Koelle
    affiliations:
      - ref: aiu
    orcid: 0000-0003-2810-1404
    email: rainer.koelle@eurocontrol.int
    role: 
      - editing
  - name: Quinten Goens
    affiliations:
      - ref: aiu
    orcid: 0000-0003-2187-1924
    email: quinten.goens@eurocontrol.int
    role: 
      - editing
affiliations:
  - id: aiu
    name: EUROCONTROL
    department: Aviation Intelligence Unit
    city: Brussels
    country: Belgium
  - id: fake
    name: ACME
    department: Best Tricks
    city: Los Angeles
    country: USA
bibliography: media/references.bib
acronyms:
  insert_loa: false
  fromfile:
    - ./media/acronyms.yml
editor: 
  markdown: 
    wrap: 72
---
```{r}
```
